### 2019-06-27 Manuscript/Manuscript.tex

\begin{itemize}
    \item lithologic mask
\end{itemize}

>>>>

\begin{figure}
    \centering
    \includegraphics{Manuscript/Figures/regolith_schematic.pdf}
    \caption{Growth of the broader Indonesia archipelago. Past shorelines are shown in A with resultant area estimates summarized in B. A significant increase in area over the past 5 million years is coincident with cooling and the onset of Northern Hemisphere glaciation as reflected in the benthic oxygen isotope record in C \cite{Zachos2008a}.}
    \label{fig:my_label}
\end{figure}
